A systematic comparison of chloroplast genome assembly tools

### 2020-08-21 manuscript/additionalfile1.tex
State for resubmission 2

\title{The landscape of chloroplast genome assembly
tools}
\subtitle{Supplemental material}
\author{\parbox{\textwidth}{\centering{}Jan A Freudenthal, Simon Pfaff, Niklas Terhoeven, Arthur Korte, Markus J Ankenbrand and Frank Förster}}
\date{}
\maketitle
\listoftables

\begin{table}[ht]
\caption{Sequencing Read Archive and Genbank accessions for novel chloroplast genomes}
\label{tab:accessions_suppl}
\centering
\begin{tabular}{p{4.5cm}ccc}\toprule
Species & SRA-Accession & Assembler & Genbank-Accession \\\midrule
\emph{Antirrhinum majus \emph{subsp.} Striatum} & ERR2744402 & \go{} & - \\
\emph{Antirrhinum majus \emph{var.} pseudomajus} & ERR2744401 & \go{} & - \\
\emph{Arachis magna} & SRR8481359 & \go{} & - \\
\emph{Boechera stricta} & SRR6821984 & \np{} & - \\
\emph{Buddleja globosa} & SRR6331521 & \go{} & - \\
\emph{Congea tomentosa} & SRR6940055 & \go{} & - \\
\emph{Cucurbita argyrosperma} & SRR2531270 & \go{} & - \\
\emph{Cucurbita ecuadorensis} & SRR2531278 & \go{} & - \\
\emph{Cucurbita lundelliana} & SRR2531284 & \go{} & - \\
\emph{Cucurbita okeechobeensis} & SRR2531280 & \go{} & - \\
\emph{Cucurbita pedatifolia} & SRR2531289 & \go{} & - \\
\emph{Cuscuta campestris} & ERR1917165 & \go{} & - \\
\emph{Erysimum baeticum} & SRR7223704 & \go{} & - \\
\emph{Erysimum nevadense} & SRR7223710 & \go{} & - \\
\emph{Garrya flavescens} & SRR2401791 & \go{} & - \\
\emph{Gerbera hybrid cultivar} & SRR2154064 & \go{} & - \\
\emph{Leucanthemum vulgare} & ERR3089127 & \go{} & - \\
\emph{Petraeovitex bambusetorum} & SRR6940081 & \go{} & - \\
\emph{Pityopsis graminifolia \emph{var.} Graminifolia} & SRR4457826 & \go{} & - \\
\emph{Pityopsis graminifolia \emph{var.} tenuifolia} & SRR4457835 & \go{} & - \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\title{A systematic comparison of  chloroplast genome assembly tools}
\subtitle{Supplemental material}
\author{\parbox{\textwidth}{\centering{}Jan A Freudenthal, Simon Pfaff, Niklas Terhoeven, Arthur Korte, Markus J Ankenbrand and Frank Förster}}
\date{}
\maketitle
\listoftables

\begin{landscape}
\setlength{\LTcapwidth}{1.5\textwidth}
\begin{table}[ht]
\caption{Sequencing Read Archive and Genbank accessions for novel chloroplast genomes}
\label{tab:accessions_suppl}
\centering
\begin{tabular}{lcccc}\toprule
Species & SRA-Accession & Assembler & Uses & Genbank-Accession \\\midrule
\emph{Antirrhinum majus \emph{subsp.} Striatum} & ERR2744402 & \go{} & ornamental plant & - \\
\emph{Antirrhinum majus \emph{var.} pseudomajus} & ERR2744401 & \go{} & ornamental plant & - \\
\emph{Arachis magna} & SRR8481359 & \go{} & - & - \\
\emph{Boechera stricta} & SRR6821984 & \np{} & - & - \\
\emph{Buddleja globosa} & SRR6331521 & \go{} & folk medicine & - \\
\emph{Congea tomentosa} & SRR6940055 & \go{} & - & - \\
\emph{Cucurbita argyrosperma} & SRR2531270 & \go{} & crop plant & - \\
\emph{Cucurbita ecuadorensis} & SRR2531278 & \go{} & - & - \\
\emph{Cucurbita lundelliana} & SRR2531284 & \go{} & - & - \\
\emph{Cucurbita okeechobeensis} & SRR2531280 & \go{} & - & - \\
\emph{Cucurbita pedatifolia} & SRR2531289 & \go{} & - & - \\
\emph{Cuscuta campestris} & ERR1917165 & \go{} & - & - \\
\emph{Erysimum baeticum} & SRR7223704 & \go{} & - & - \\
\emph{Erysimum nevadense} & SRR7223710 & \go{} & - & - \\
\emph{Garrya flavescens} & SRR2401791 & \go{} & - & - \\
\emph{Gerbera hybrid cultivar} & SRR2154064 & \go{} & - & -\\
\emph{Leucanthemum vulgare} & ERR3089127 & \go{} & ornamental plant & - \\
\emph{Petraeovitex bambusetorum} & SRR6940081 & \go{} & - & - \\
\emph{Pityopsis graminifolia \emph{var.} Graminifolia} & SRR4457826 & \go{} & ornamental plant & - \\
\emph{Pityopsis graminifolia \emph{var.} tenuifolia} & SRR4457835 & \go{} & ornamental plant & - \\
\bottomrule
\end{tabular}
\end{table}
\end{landscape}
